---
title: "2_Analyses_and_visuals"
author: "ASM"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r call in libraries and clean data, include=FALSE}
library(here)
library(dplyr)
library(stringr)
library(Hmisc)
library(corrplot)
library(zoo)
library(eyetrackingR)
library(psych)
library(QuantPsyc)
library(lmerTest)
library(DHARMa)
library(performance)
library(psych)
library(tidyverse)

load(here("archival_KBH_anonimyzed/kbh_w_items.Rda"))

```


```{r}
####### Only keep kids with at least 50% of interest period looking AND who have at least 25% of trials
## Total trials for each study is usually 12 (CogMisp, Mix), except CompMix, CompLearn with 16, LearnMix with 6

trial_cutoff <- kbh_w_items %>%
  group_by(recording_name) %>%
  distinct(studio_project_name, trial_number) %>%
  count(studio_project_name, recording_name) %>%
  group_by(studio_project_name) %>%
  rename(n_trials_subject = n) %>%
  mutate(max_trials_study = max(n_trials_subject)) %>%
  distinct(studio_project_name, max_trials_study)

n_subjects_original <- n_distinct(kbh_w_items$recording_name)
  
trackloss_cleaned <- kbh_w_items %>%
  #for each kid in each trial,
  group_by(recording_name, trial_number) %>%
  #filter to interest period
  filter(noun_onset>= 360 & noun_onset <= 3000) %>%
  #get trackloss percentage
  mutate(trackloss_pct = sum(trackloss == TRUE)/n(),
         trackloss_cutoff = case_when(trackloss_pct <.5 ~ "keep",
                                      trackloss_pct >= .5 ~ "exclude")) %>%
  ungroup() %>%
  distinct(recording_name, trial_number, trackloss_pct, trackloss_cutoff) %>%
  filter(trackloss_cutoff == "keep") %>%
  group_by(recording_name) %>%
  mutate(n_valid_trials_subject = n()) %>%
  ungroup() %>%
  dplyr::select(recording_name, trial_number, trackloss_pct, n_valid_trials_subject)

n_subjects_after_trackloss_exclusion <- n_distinct(trackloss_cleaned$recording_name)
  
analysis_dataset <- kbh_w_items %>%
  right_join(trackloss_cleaned) %>%
  left_join(trial_cutoff) %>%
  mutate(trial_n_cutoff = round(max_trials_study*.25, digits = 0)) %>%
  filter(n_valid_trials_subject >= trial_n_cutoff) %>%
  ungroup()

n_subjects_after_trackloss_and_trials_exclusion <- n_distinct(analysis_dataset$recording_name) #6 kids lost from these exclusions

```

#Make variables

```{r calculate all the different dependent variables}

###### First, create variables that will be useful for the calculations below ## TRY TO DO IT IN THE SAME DATA SET
initial_looks <- analysis_dataset %>%
  filter(noun_onset >= 260 & noun_onset < 360) %>%
  group_by(recording_name, trial_number, media_name) %>% 
     summarise(
    distractor_count = sum(distractor),
    target_count = sum(target),
    trackloss_count = sum(trackloss)
     )%>%
  mutate(initial_look = case_when(target_count >0 ~ "target", #if the child *ever* looks to target during first 100 ms, then counted as initial target look
                                  distractor_count/(distractor_count+trackloss_count) >=0.5 ~ "distractor",
                                  TRUE ~ "neither"))

analysis_dataset <- left_join(analysis_dataset, initial_looks, by= c("recording_name", "trial_number", "media_name"))

#We are considering distractor initial trials as trials where in the first 100 ms ofr the analyses window the child looked at the distractor at least 50% of the time and never looked to target.


#Mix 20 S052 has 23 rows for trials other than trial 1 with no data—remove these here, try to figure out why this happened

analysis_dataset <- analysis_dataset %>%
  filter(!(recording_name == "Mix_20_S52" & trial_number > 1))

#1. Proportion looking to target

prop_looking_by_trial <- analysis_dataset %>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  group_by(recording_name, subject_id, trial_number, media_name, 
           age_months, exp_to_target_lang) %>%
  summarise(samples_target=sum(target, na.rm = T),
            samples_distractor=sum(distractor, na.rm = T))%>%
  mutate(prop_looking = samples_target/(samples_target + samples_distractor)) %>%
  ungroup()

prop_looking_by_subject <- prop_looking_by_trial %>%
  group_by(recording_name) %>%
  summarise(prop_looking = mean(prop_looking)) %>%
  ungroup()

#2. Proportion looking difference 
#Within a pair of pictures A and B, the fixation to picture A relative to B when A was the target, minus the fixation #to A when A was the distractor.

prop_looking_diff_by_item <- analysis_dataset %>%
  ungroup()%>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  dplyr::select(recording_name, recording_timestamp, target_word, distractor_word, target, distractor)%>%
  pivot_longer(c(target_word, distractor_word), names_to = "word_type", values_to = "word") %>%
  mutate(looking = case_when(word_type == "target_word" & target == TRUE ~ TRUE,
                             word_type == "distractor_word" & distractor == TRUE ~ TRUE,
                             TRUE ~ FALSE)) %>%
  group_by(recording_name, word_type, word) %>%
  #what percent of the time when x is target are kids looking at x, what percent of the time when x is distractor are kids looking at x
  summarise(prop_looking = sum(looking == T, na.rm = T)/n()) %>%
  pivot_wider(names_from = "word_type", values_from = "prop_looking") %>%
  filter(!is.na(target_word) & !is.na(distractor_word)) %>%
  mutate(prop_looking_diff = target_word - distractor_word) %>%
  dplyr::select(recording_name, target_word = word, prop_looking_diff) %>%
  ungroup() 

prop_looking_diff_by_subject <- prop_looking_diff_by_item %>%  
  group_by(recording_name) %>% #Calculating this variable by subject instead of by trial for the correlation matrix.
  summarise(prop_looking_diff = mean(prop_looking_diff)) %>%
  ungroup() #only 165 kids have data for this variable, because they didn't have enough data/trials included with both words of each yoked pair

  
#3. Number of fixations
### Total number of fixations to the target during the window of analyses.
#### Question: What is considered a fixation? --> In TOBII we kept only valid fixations (as in Mills-Smith, 2016), they also excluded by subject and by trial (which we will do).

#we defined fixations as the number of consecutive runs within a trial where looks were in the target for at least 200ms while getting rid of short bouts of trackloss (17 to 38 ms)

# Group by subject and summarize consecutive TRUE values in target column - we are counting how many consecutive groups of 12 rows of TRUE target looks there are per trial, which is around 200 ms of looking. We are counting each group of 200 ms of looking as one fixation.
# 
# sampling_quadrants <- tibble(x_min = c(0, 481, 0, 481, 961, 1441, 961, 1441),
#                              x_max = c(480, 960, 480, 960, 1440, 1920, 1440, 1920),
#                              y_min = c(0, 0, 541, 541, 0, 0, 541, 541),
#                              y_max = c(540, 540, 1080, 1080, 540, 540, 1080, 1080),
#                              sampling_quadrant = c(1, 2, 3, 4, 1, 2, 3, 4))

# sampling_fixations_total <- analysis_dataset %>%
#   ungroup() %>%
#   filter(noun_onset >= 360 & noun_onset <= 3000) %>%
#   #create sampling quadrants
#   mutate(sampling_quadrant = case_when(gaze_point_x > 0 & gaze_point_x <=480 & gaze_point_y > 0 & gaze_point_y <= 540 ~ 1,
#                                        gaze_point_x >= 481 & gaze_point_x <=960 & gaze_point_y > 0 & gaze_point_y <= 540 ~ 2,
#                                        gaze_point_x > 0 & gaze_point_x <=480 & gaze_point_y >= 541 & gaze_point_y <= 1080 ~ 3,
#                                        gaze_point_x >= 481 & gaze_point_x <=960 & gaze_point_y >= 541 & gaze_point_y <= 1080 ~ 4,
#                                        gaze_point_x >= 961 & gaze_point_x <=1440 & gaze_point_y > 0 & gaze_point_y <= 540 ~ 5,
#                                        gaze_point_x >= 1441 & gaze_point_x <=1920 & gaze_point_y > 0 & gaze_point_y <= 540 ~ 6,
#                                        gaze_point_x >= 961 & gaze_point_x <=1440 & gaze_point_y >= 541 & gaze_point_y <= 1080 ~ 7,
#                                        gaze_point_x >= 1441 & gaze_point_x <=1920 & gaze_point_y >= 541 & gaze_point_y <= 1080 ~ 8)) %>%
#   group_by(recording_name, trial_number) %>%
#   #come back to this.... current idea is to check if coordinates are within 20 px of each other and count those as a cluster
#   mutate(cluster_id = case_when(row_number() == 1 ~ 1,
#                                 (gaze_point_x <= lag(gaze_point_x) + 20 | gaze_point_x >= lag(gaze_point_x) + 20) & (gaze_point_y <= lag(gaze_point_y) + 20 | gaze_point_y >= lag(gaze_point_y) + 20)) ~ max(cluster_id, na.rm = T),
#          TRUE ~ max(cluster_id, na.rm = T) + 1)
  # group_by(recording_name, trial_number) %>%
  # mutate(trackloss_group_id = data.table::rleid(trackloss)) %>%
  # group_by(trackloss_group_id, recording_name, trial_number) %>%
  # mutate(num_consec_trackloss_rows = n()) %>%
  # ungroup() %>%
  # filter(trackloss == FALSE | (trackloss == TRUE & num_consec_trackloss_rows >= 2)) %>%
  # group_by(recording_name, trial_number, sampling_quadrant) %>% 
  # mutate(looking_stretch_id = data.table::rleid(target)) %>%
  # group_by(recording_name, trial_number, looking_stretch_id, sampling_quadrant) %>%
  # mutate(row = row_number(), 
  #        multi_of_twelve = case_when(row %% 12 == 0 & target == TRUE ~ "fixation")) %>% 
  
  
  # 
  # group_by(#trial_number, media_name keep this to calculate variable by trial instead of by subject.
  #   recording_name, subject_id) %>%
  # summarise(number_sampling_fixations = sum(multi_of_twelve == "fixation", na.rm = T)) %>%
  # ungroup()

#For this one, stretches of same looks are counted as one fixation
fixations_total_by_trial <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  group_by(recording_name, trial_number) %>%
  mutate(trackloss_group_id = data.table::rleid(trackloss)) %>%
  group_by(trackloss_group_id, recording_name, trial_number) %>%
  mutate(num_consec_trackloss_rows = n()) %>%
  ungroup() %>%
  filter(trackloss == FALSE | (trackloss == TRUE & num_consec_trackloss_rows >= 2)) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #filter to fixations of at least 12 rows or ~ 200 ms
  filter(n() >= 12) %>%
  #filter to target fixations
  filter(target == TRUE) %>%
  distinct(recording_name, trial_number, looking_stretch_id) %>%
  group_by(recording_name, trial_number) %>%
  summarise(number_fixations = n()) %>%
  ungroup()

fixations_total_by_subject <- fixations_total_by_trial %>%
  group_by(recording_name) %>%
  summarise(number_fixations = sum(number_fixations)) %>%
  ungroup()
  
#4. Correct first shift to target
#On trials where infants were fixated on the distractor upon hearing the target word (i.e., distractor-initial trials), does the kid shift to the target picture within the 300–1,800 ms window following target word onset, as a proportion of all distractor-initial trials.
  

first_shift_target <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 1800) %>% #Keeping the shorter window to be consistent with Fernald

  
    #Grouping and summarizing to get by subject by trial flagging of whether there was switching or not.
     group_by(recording_name, subject_id, trial_number, media_name, initial_look) %>%  
  summarise(target = sum(target, na.rm = T),
            distractor =  sum(distractor, na.rm = T)) %>% #Counting how many looks to target and distractor by timeslice grouped by target or distractor initial trials.
  ungroup() %>%
  mutate(correct_shift = case_when(initial_look == "target" & distractor ==0 ~ TRUE,
                                   initial_look == "distractor" & target >0 ~ TRUE,
                                   TRUE~FALSE)) #Making a column to calculate correct shifts. We defined correct shift as never looking to the distractor on target initial trial, or switching to the taget on distractor initial trials

prop_shifts_distractor_initial_by_trial <- first_shift_target %>%
    filter(initial_look == "distractor") 

prop_shifts_distractor_initial_by_subject <- prop_shifts_distractor_initial_by_trial %>%
  group_by(recording_name) %>%
    summarise(prop_shift_distractor_initial = sum(correct_shift == TRUE)/n())
  
prop_shifts_target_initial_by_trial <- first_shift_target %>%
    filter(initial_look == "target") 

prop_shifts_target_initial_by_subject <- prop_shifts_target_initial_by_trial %>%
  group_by(recording_name) %>%
    summarise(prop_shift_target_initial = sum(correct_shift == TRUE)/n())
  

#5. Reaction time

#do we want the latency from noun onset (0) or from window of analysis(360)? Right now using window of analysis

RT_by_trial <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 1800) %>% #Keeping the shorter window to be consistent with Fernald
    #Grouping and summarizing to get by subject by trial flagging of whether there was switching or not.
  filter(initial_look == "distractor") %>%
  filter(target == TRUE) %>%
  group_by(trial_number, media_name, recording_name, subject_id, initial_look, target) %>%
  slice_head() %>%
  mutate(latency_to_switch = noun_onset - 360) %>%
  ungroup() %>%
  dplyr::select(recording_name, trial_number, latency_to_switch) 

RT_by_subject <- RT_by_trial %>%
  group_by(recording_name) %>%
  summarise(mean_RT = mean(latency_to_switch, na.rm = T)) %>%
  ungroup()


#6. Total number of switches between AOIs

number_of_switches_by_trial <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  #for this one, get rid of track loss rows
  filter(trackloss == FALSE) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #keep stretches that are at least 200 ms or 12 rows
  filter(n() >= 12) %>%
  mutate(where_looking = case_when(target == TRUE ~ "target",
                                   distractor == TRUE ~ "distractor",
                                   TRUE ~ "neither")) %>%
  filter(where_looking != "neither") %>%
  distinct(recording_name, trial_number, looking_stretch_id, where_looking, media_name, subject_id) %>%
  group_by(recording_name, trial_number) %>%
  mutate(AOI_switches = case_when(lag(where_looking) == "target" & where_looking == "distractor" ~ 1,
                            lag(where_looking) == "distractor" & where_looking == "target" ~ 1)) %>%
  group_by(recording_name, trial_number) %>%
  summarise(total_aoi_switches = sum(AOI_switches, na.rm = T)) %>%
  ungroup()

number_of_switches_by_subject <- number_of_switches_by_trial %>%
  group_by(recording_name) %>%
  summarise(total_aoi_switches = sum(total_aoi_switches, na.rm = T)) %>%
  ungroup()
  
  
#7. Mean latency of refixation during trial - COME BACK TO THIS ------- We decided to eliminate this one because our studies don't have a central image from which to refixate, and when we tried adding a narrow central strip, no one was looking there.
#Mean latency of correct saccadic shifts from the center to the peripheral target (refixations) during the trial. 
#I would need to calculate the center point (shouldn't be too hard)
# 
# kbh_data_center <- arch_final%>%
#   group_by(studio_project_name, studio_test_name, trial_number, recording_name)%>%
#   mutate(trial_from_zero = recording_timestamp-min(recording_timestamp))%>%
#   group_by(studio_project_name)%>%
#   mutate(noun_onset = case_when(studio_project_name=="CompMix-36"~trial_from_zero-3000, #Substracting noun onset to normalize
#                                 studio_project_name=="LearnMix-36"~trial_from_zero-4500,
#                                 studio_project_name=="Mix-20"~trial_from_zero-5400,
#                                 studio_project_name=="Mix-14"~trial_from_zero-5400,
#                                 studio_project_name=="CogMisp-24"~trial_from_zero-1500))%>%
#   ungroup()%>%
#   rename(target_side=target, distractor_side=distractor,
#          gaze_point_x= gaze_point_x_adc_spx, 
#          gaze_point_y = gaze_point_y_adc_spx)%>%
#   mutate(trackloss = case_when(gaze_point_x<0 ~ TRUE,
#                                gaze_point_x> 1920 ~ TRUE,
#                                gaze_point_y<0 ~ TRUE,
#                                gaze_point_y > 1200 ~ TRUE,
#                                is.na(gaze_point_x) ~ TRUE,
#                                is.na(gaze_point_y) ~ TRUE,
#                                is.na(validity_left) ~ TRUE,
#                                is.na(validity_right) ~ TRUE,
#                                validity_left > 1 ~ TRUE,
#                                validity_right > 1 ~ TRUE,
#                                TRUE~ FALSE)) %>% #MAKE VISUALIZATIONS ABOUT TRACKLOSS FOR SANITY CHECK
#   mutate(target = case_when(gaze_point_x >= target_x_min&gaze_point_x <= target_x_max&gaze_point_y >= target_y_min&gaze_point_y <= target_y_max~TRUE, 
#                             TRUE~FALSE)) %>%
#   mutate(distractor = case_when(gaze_point_x >= distractor_x_min&gaze_point_x <= distractor_x_max&gaze_point_y >= distractor_y_min&gaze_point_y <= distractor_y_max~TRUE, 
#                                  TRUE ~ FALSE)) %>%
#   mutate(looks_to_center = case_when(gaze_point_x >= 950 & gaze_point_x <= 970 &gaze_point_y >= 0&gaze_point_y <= 1080 ~ TRUE,
#                                      TRUE~ FALSE)) %>% #creating a looks to center column
# mutate(where_looking = case_when(target == TRUE & looks_to_center == FALSE~ "target",
#                          target == TRUE & looks_to_center == TRUE~ "center",
#                          distractor == TRUE & looks_to_center == TRUE~ "center",
#                          distractor == TRUE & looks_to_center == FALSE~ "distractor",
#                          target == FALSE & distractor == FALSE & looks_to_center == TRUE ~ "center",
#                          TRUE ~ "neither"))
# 
# 
# mean_latency_refixation <- kbh_data_center %>%
#   filter(noun_onset >= 360 & noun_onset <= 3000) %>%
#   group_by(recording_name, trial_number) %>%
#   dplyr::select(looks, media_name, studio_project_name, studio_test_name, trial_number, recording_name, recording_timestamp, where_looking) %>%
#   mutate(looking_area_id = data.table::rleid(where_looking)) %>%
#   group_by(recording_name, trial_number, looking_area_id) %>%
#   mutate(how_long_looking_area = n(),
#          length_center_look = case_when(where_looking == "center" ~ how_long_looking_area))
  
  
#   
#   filter(looks %in% c("target", "center")) %>% #filtering out disctractor looks because I am only interest in latency to look to taget
# group_by(recording_name, media_name) %>%
#   filter("target" %in% looks & "center" %in% looks) %>% #keeping only trials where there were looks to target and to center
#   arrange()%>%
#  filter(!(looks == "target" & lag(looks) == "target")) %>% #getting rid of consecutive target looks because I am not interested in duration of looks to target I am interested in duration of looks to center before the switch.
#  ungroup() %>%
#   mutate(consecutive_looks_center= looks == "center" & lag(looks) == "center") %>%
#     group_by(recording_name, media_name, consecutive_looks_center, looks) %>%
#   reframe(total_time = sum(recording_timestamp)) %>%
#       ungroup() 
# 
# mean_latency_refixation2 <- mean_latency_refixation %>%
# group_by(recording_name, media_name) %>%
#    filter(looks == "center" & lead(looks) == "target") # not working
# 
#   summarise(time_to_refixate = diff(total_time))
 

#8. Mean fixation duration during trial
#Mean duration of fixations during the window of analysis within a trial. Mean by subject by trial?

mean_fixation_dur_by_trial <- analysis_dataset %>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  group_by(recording_name, trial_number) %>%
  mutate(trackloss_group_id = data.table::rleid(trackloss)) %>%
  group_by(trackloss_group_id, recording_name, trial_number) %>%
  mutate(num_consec_trackloss_rows = n()) %>%
  ungroup() %>%
  filter(trackloss == FALSE | (trackloss == TRUE & num_consec_trackloss_rows >= 2)) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #filter to fixations of at least 12 rows or ~ 200 ms
  filter(n() >= 12) %>%
  filter(target == TRUE) %>%
  group_by(recording_name, trial_number, media_name, looking_stretch_id) %>%
  summarise(length_of_looks = n()) %>%
  mutate(duration_of_look = length_of_looks*(1000/60)) %>%
  group_by(recording_name, trial_number) %>%
  summarise(duration_of_look = mean(duration_of_look, na.rm = T)) %>%
  ungroup()

mean_fixation_dur_by_subject <- mean_fixation_dur_by_trial %>% 
  group_by(recording_name) %>%
  summarise(duration_of_look = mean(duration_of_look, na.rm = T)) %>%
  ungroup()



#When you have time make some of the calculations by hand to make sure the duration is correct.
#I guess here is by subject the mean duration. But check on the paper.


#9. Proportion of fixation duration (better named target divergence time)
#The target divergence time measure is defined as the time at which fixations to the “target” object diverges from fixations to the “distractor”. point-by-point t-tests at each 10 ms bin between mean looking proportions to the target object and mean looking proportions to the distractor object were calculated. the time point reported is the earliest time point that a minimum of five consecutive two tailed t-tests with an alpha level of p < .05 indicate a significant difference between the fixation to the target compared to distractor

#What we need to do in our research: By participant, collapsing across trials average prop looking to target and average proportion looking to distractor eavery 17ms (or whatever or bin size is). So at that stage the participant has 2 columns with 8 rows (1 row per trial), one column for the average prop looks to target, one for the average prop looks to distractor. THEN we do a t test between column A and B, so we get column C that again has 8 rows (this is a rowwise t test, bonferroni corrected I guess). Then we summarize to get a single number per participant. that number is the ms slice at which 5 (?) t-tests are p>0.05.


#Get average looking to target and looking to distractor for each 220-ms time bin (the reference paper used 10-ms time bins, but their eyetracker sampled every 2ms and ours only did ever 16-17 ms)

divergence_point <- analysis_dataset %>%
  filter(noun_onset>= -2000 & noun_onset <= 3000)%>%
  #make timestamp that is offset by the time it takes to initiate a look, related to the noun onset
  mutate(timestamp_zero_interest_period = noun_onset - 360) %>%
  ungroup()%>%
  group_by(recording_name, trial_number, media_name, age_months) %>%
  #Need to align timestamps for each trial, so make the one closest to 0 equal zero and then add the eyetracker frame rate for each row
  mutate(new_noun_onset = case_when(abs(noun_onset) == min(abs(noun_onset)) ~ 0)) %>% 
  dplyr::select(recording_name, trial_number, recording_timestamp, trial_from_zero, noun_onset, new_noun_onset, target, distractor, trackloss, age_months) %>% 
  mutate(parallel_timestamp = (row_number() - which(new_noun_onset == 0))*(1000/60),
         parallel_timestamp = round(parallel_timestamp)) %>%
  dplyr::select(media_name, recording_name, trial_number, parallel_timestamp, target, distractor, trackloss, age_months) %>%
  pivot_longer(c(target, distractor), names_to = "aoi", values_to = "value") %>%
  arrange(recording_name, trial_number, aoi, parallel_timestamp) %>%
  mutate(value = as.numeric(value)) %>%
  filter(trackloss == FALSE) %>%
  ungroup() %>%
  mutate(age_group = case_when(age_months >= 14 & age_months < 21 ~ "14-20",
                               age_months >= 21 & age_months < 31 ~ "21-30",
                               age_months >= 31 & age_months < 51 ~ "31-48"))

divergence_plot_data <- divergence_point %>%
  group_by(recording_name, aoi, parallel_timestamp, age_group) %>%
  summarise(mean_fixation = mean(value))

#This takes a little while to run because of the bootstrapping
divergence_plot <- ggplot(divergence_plot_data, aes(x=parallel_timestamp, y=mean_fixation, colour=aoi)) +
  geom_vline(xintercept=0, linetype="dashed", colour="gray28") +
  stat_summary(fun.data=mean_cl_boot, aes(fill=aoi),
               geom="ribbon", alpha=.2, linetype="blank") +
  stat_summary(fun=mean, geom="path", 
               aes(group=aoi, linetype=aoi), size=.7) + facet_wrap(~age_group)

divergence_point_stat <- divergence_point %>%
  #reduce the time span for calculating stats since the bootstrapping takes a while.
  filter(parallel_timestamp >= -500 & parallel_timestamp <= 2500)

#Apply statistical test to each time point
divergence_p_table <- divergence_point_stat %>%
  # select only rows in the dataframe where a fixation occurred
  filter(value == 1) %>%
  # label fixations that were on the target as 1 and as 0 otherwise,
  mutate(looking_to_target = ifelse(aoi == "target", 1, 0)) %>%
  # we want to test for each timepoint at each age group
  group_by(parallel_timestamp, age_group) %>%
  # apply logistic regression and extract z-values
  summarise(z = summary(lme4::glmer(looking_to_target ~ 1 +
  (1|recording_name), family="binomial",
  control=lme4::glmerControl(calc.derivs=FALSE)))$coefficients[1,3]) %>%
  # add p-values
  mutate(p = pnorm(-abs(z))*2) 

# Set alpha level and calculate Bonferroni correction
alpha           <- 0.05
N_tests         <- length(unique(divergence_point_stat$parallel_timestamp))
alpha_corrected <- alpha/N_tests

# Find the earliest timepoint with a significant uncorrected p-value
(uncorr <- divergence_p_table %>%
  group_by(age_group) %>%
  # extract positive z-scores ("target advantage") and significant p-values
  filter(z > 0, p < alpha) %>% 
  # extract the earliest significant p-value and its timepoint 
  slice(1))

# Find the earliest timepoint that survives the Bonferroni correction
(bnf <- divergence_p_table %>%
  group_by(age_group) %>%
  filter(z > 0, p < alpha_corrected) %>% 
  slice(1))

# Find the earliest timepoint after FDR control
(fdr <- divergence_p_table %>%
  group_by(age_group) %>%
  # apply FDR control from `stats` package
  mutate(p_fdr = stats::p.adjust(p, method = "BY", n = length(p))) %>%
  filter(z > 0, p_fdr < alpha) %>%
  slice(1))

plot_points <- tibble(correction = c(rep("Uncorrected", 3), rep("Bonferroni", 3), rep("FDR", 3)),
                      age_group = rep(c("14-20", "21-30", "31-48"),3),
                      parallel_timestamp = c(uncorr$parallel_timestamp, bnf$parallel_timestamp, fdr$parallel_timestamp),
                      mean_fixation = .5,
                      aoi = "target")

overall_divergence_plot <- ggplot(divergence_plot_data, aes(x=parallel_timestamp, y=mean_fixation, colour=aoi)) +
  geom_vline(xintercept=0, linetype="dashed", colour="gray28") +
  stat_summary(fun.data=mean_cl_boot, aes(fill=aoi),
               geom="ribbon", alpha=.2, linetype="blank") +
  stat_summary(fun=mean, geom="path", 
               aes(group=aoi, linetype=aoi), size=.7) +
  facet_wrap(~age_group) +
  geom_point(data = plot_points, color = "black", aes(shape = plot_points$correction))


#Apply statistical test to each time point for each kid
divergence_p_table_by_subject <- divergence_point_stat %>%
  # select only rows in the dataframe where a fixation occurred
  filter(value == 1) %>%
  # label fixations that were on the target as 1 and as 0 otherwise,
  mutate(looking_to_target = ifelse(aoi == "target", 1, 0)) %>%
  # we want to test for each timepoint for each subject
  group_by(parallel_timestamp, recording_name) %>%
  # apply logistic regression and extract z-values
  summarise(z = summary(glm(looking_to_target ~ 1, family="binomial"))$coefficients[1,3]) %>%
  # add p-values
  mutate(p = pnorm(-abs(z))*2) 

# Find the earliest timepoint with a significant uncorrected p-value
(uncorr_by_subject <- divergence_p_table_by_subject %>%
  group_by(recording_name) %>%
  # extract positive z-scores ("target advantage") and significant p-values
  filter(z > 0, p < alpha) %>% 
  # extract the earliest significant p-value and its timepoint 
  slice(1))

# Find the earliest timepoint that survives the Bonferroni correction ----------- Looks like when you split by subject, there isn't enough data for the corrected p values to be significant, so statistically, individual children don't have a divergence point after correcting
(bnf_by_subject <- divergence_p_table_by_subject %>%
  group_by(recording_name) %>%
  filter(z > 0, p < alpha_corrected) %>% 
  slice(1))

# Find the earliest timepoint after FDR control
(fdr_by_subject <- divergence_p_table_by_subject %>%
  group_by(recording_name) %>%
  # apply FDR control from `stats` package
  mutate(p_fdr = stats::p.adjust(p, method = "BY", n = length(p))) %>%
  filter(z > 0, p_fdr < alpha) %>%
  slice(1))

#10. Pupil dilation
#Baseline pupil size in the 200ms before noun onset and then subtracted the baseline from the pupil size measurements on each trial.
#In Liz's paper they contrasted time slice by time slice across two conditions, but here we don't have switched and same language conditions. I'll do average size at baseline and avg size after noun onset for now. But then talk with team about it.


pupil_dilation <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset>= -200 & noun_onset <= 500)%>%
mutate(pupil_period = case_when(noun_onset >= -200 & noun_onset <= 0 ~ "baseline",
                                TRUE ~ "post_onset"))%>% 
  dplyr::select(recording_timestamp, subject_id, recording_name, trial_number, media_name, pupil_period, pupil_right, pupil_left) %>%
  mutate(two_pupil_mean = case_when(is.na(pupil_left) & is.na(pupil_right) ~ NA,
                                         is.na(pupil_left)  ~ pupil_right,
                                         is.na(pupil_right) ~ pupil_left,
                                         TRUE ~ (pupil_left + pupil_right)/2)) %>%
  filter(!is.na(two_pupil_mean))

#The next steps are confusing to me.Should we average baseline pupil? Should we contrast each post onset time slice to a partricular baseline time slice? We could use mean dilation, peak dilation (or peak amplitude), and/or peak latency (i.e., the time between onset and peak pupil dilation). The problem with mean dilation is that the baseline has less sampling than the post-onset. Could we do peak dilation of baseline vs. peak dilation post onset? Or peak dilation but from which baseline point? from peak? We will for sure do GCA's as extra analyses

#Peak dilation
peak_dilation_by_trial <- pupil_dilation %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period) %>%
  summarise(peak_pupil = max(two_pupil_mean)) %>%
  pivot_wider(names_from = pupil_period, values_from ="peak_pupil")%>%
  mutate(peak_pupil_size_difference = post_onset - baseline) %>% #difference in peak pupil points
  filter(!is.na(peak_pupil_size_difference)) %>%
  rename(max_pupil_baseline = baseline,
         max_pupil_post_onset = post_onset) %>%
  ungroup()

peak_dilation_by_subject <- peak_dilation_by_trial %>%
  group_by(recording_name) %>%
  summarise(peak_pupil_size_difference = mean(peak_pupil_size_difference)) %>%
  ungroup() 
  
#Mean dilation
mean_dilation_by_trial <- pupil_dilation %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period) %>%
  summarise(mean_pupil = mean(two_pupil_mean, na.rm = T)) %>%
  pivot_wider(names_from = pupil_period, values_from ="mean_pupil")%>%
  mutate(mean_pupil_size_difference = post_onset - baseline) %>% #difference in peak pupil points
  filter(!is.na(mean_pupil_size_difference)) %>%
  rename(mean_pupil_baseline = baseline,
         mean_pupil_post_onset = post_onset) %>%
  ungroup() 

mean_dilation_by_subject <- mean_dilation_by_trial %>%
  group_by(recording_name) %>%
  summarise(mean_pupil_size_difference = mean(mean_pupil_size_difference)) %>%
  ungroup()
  


#peak latency
peak_pupil_latency_by_trial <- pupil_dilation %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period) %>%
  slice(which.max(two_pupil_mean)) %>%
  dplyr::select(recording_name, pupil_period, peak_time_stamp = recording_timestamp) %>%
  group_by(trial_number, recording_name) %>%
  summarise(peak_pupil_latency = diff(peak_time_stamp)) %>%
  ungroup()

peak_pupil_latency_by_subject <- peak_pupil_latency_by_trial %>%
  group_by(recording_name) %>%
  summarise(peak_pupil_latency = mean(peak_pupil_latency))


#11. Duration of first look
### Duration of the first look recorded toward a particular AOI. - To target specifically, with at least 200 ms fixation length

first_look_duration_by_trial <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  mutate(row = row_number()) %>% 
  mutate(where_looking = case_when(target == TRUE ~ "target",
                                   distractor == TRUE ~ "distractor",
                                   TRUE ~ "neither")) %>%
  filter(where_looking == "target") %>%
  mutate(first_look_dur = max(row_number())*(1000/60)) %>% 
  filter(first_look_dur >= 200) %>%
  group_by(trial_number, recording_name) %>%
  filter(looking_stretch_id == min(looking_stretch_id)) %>% 
  ungroup() %>%
  distinct(recording_name, trial_number, media_name, first_look_dur) %>%
  ungroup()

first_look_duration_by_subject <- first_look_duration_by_trial %>%
  group_by(recording_name) %>%
  summarise(first_look_dur = mean(first_look_dur, na.rm = T)) %>%
  ungroup()
 

```

#Split data variables

```{r}
#------------------------------------------------Calculate same variables, split by initial look location

#Split dataset by initial look location
analysis_dataset_split <- analysis_dataset %>%
  group_by(initial_look) %>%
  nest()

#1. Proportion looking to target

prop_looking_by_subject_split <- analysis_dataset %>%
  filter(noun_onset>= 360 & noun_onset <= 3000) %>%
  group_by(recording_name, age_months, exp_to_target_lang, initial_look) %>%
  summarise(samples_target=sum(target, na.rm = T),
            samples_distractor=sum(distractor, na.rm = T))%>%
  mutate(prop_looking = samples_target/(samples_target + samples_distractor)) %>%
  ungroup()


#2. Proportion looking difference 
#Within a pair of pictures A and B, the fixation to picture A relative to B when A was the target, minus the fixation #to A when A was the distractor.

prop_looking_diff_by_item_split <- analysis_dataset %>%
  ungroup()%>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  dplyr::select(recording_name, recording_timestamp, target_word, distractor_word, target, distractor, initial_look)%>%
  pivot_longer(c(target_word, distractor_word), names_to = "word_type", values_to = "word") %>%
  mutate(looking = case_when(word_type == "target_word" & target == TRUE ~ TRUE,
                             word_type == "distractor_word" & distractor == TRUE ~ TRUE,
                             TRUE ~ FALSE)) %>%
  group_by(recording_name, word_type, word, initial_look) %>%
  #what percent of the time when x is target are kids looking at x, what percent of the time when x is distractor are kids looking at x
  summarise(prop_looking = sum(looking == T, na.rm = T)/n()) %>%
  pivot_wider(names_from = "word_type", values_from = "prop_looking") %>%
  filter(!is.na(target_word) & !is.na(distractor_word)) %>%
  mutate(prop_looking_diff = target_word - distractor_word) %>%
  dplyr::select(recording_name, target_word = word, prop_looking_diff, initial_look) %>%
  ungroup() 

prop_looking_diff_by_subject_split <- prop_looking_diff_by_item_split %>%  
  group_by(recording_name, initial_look) %>% #Calculating this variable by subject instead of by trial for the correlation matrix.
  summarise(prop_looking_diff = mean(prop_looking_diff)) %>%     
  ungroup() #only 165 kids have data for this variable, because they didn't have enough data/trials included with both words of each yoked pair


#3. Fixations
#For this one, stretches of same looks are counted as one fixation
fixations_total_by_trial_split <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  group_by(recording_name, trial_number) %>%
  mutate(trackloss_group_id = data.table::rleid(trackloss)) %>%
  group_by(trackloss_group_id, recording_name, trial_number) %>%
  mutate(num_consec_trackloss_rows = n()) %>%
  ungroup() %>%
  filter(trackloss == FALSE | (trackloss == TRUE & num_consec_trackloss_rows >= 2)) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #filter to fixations of at least 12 rows or ~ 200 ms
  filter(n() >= 12) %>%
  #filter to target fixations
  filter(target == TRUE) %>%
  distinct(recording_name, trial_number, looking_stretch_id, initial_look) %>%
  group_by(recording_name, trial_number, initial_look) %>%
  summarise(number_fixations = n()) %>%
  ungroup()

fixations_total_by_subject_split <- fixations_total_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(number_fixations = sum(number_fixations)) %>%
  ungroup()


#6. Total number of switches between AOIs

number_of_switches_by_trial_split <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  #for this one, get rid of track loss rows
  filter(trackloss == FALSE) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #keep stretches that are at least 200 ms or 12 rows
  filter(n() >= 12) %>%
  mutate(where_looking = case_when(target == TRUE ~ "target",
                                   distractor == TRUE ~ "distractor",
                                   TRUE ~ "neither")) %>%
  filter(where_looking != "neither") %>%
  distinct(recording_name, trial_number, looking_stretch_id, where_looking, media_name, subject_id, initial_look) %>%
  group_by(recording_name, trial_number) %>%
  mutate(AOI_switches = case_when(lag(where_looking) == "target" & where_looking == "distractor" ~ 1,
                            lag(where_looking) == "distractor" & where_looking == "target" ~ 1)) %>%
  group_by(recording_name, trial_number, initial_look) %>%
  summarise(total_aoi_switches = sum(AOI_switches, na.rm = T)) %>%
  ungroup()

number_of_switches_by_subject_split <- number_of_switches_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(total_aoi_switches = sum(total_aoi_switches, na.rm = T)) %>%
  ungroup()
  
  
#8. Mean fixation duration during trial
#Mean duration of fixations during the window of analysis within a trial. Mean by subject by trial?

mean_fixation_dur_by_trial_split <- analysis_dataset %>%
  filter(noun_onset>= 360 & noun_onset <= 3000)%>%
  group_by(recording_name, trial_number) %>%
  mutate(trackloss_group_id = data.table::rleid(trackloss)) %>%
  group_by(trackloss_group_id, recording_name, trial_number) %>%
  mutate(num_consec_trackloss_rows = n()) %>%
  ungroup() %>%
  filter(trackloss == FALSE | (trackloss == TRUE & num_consec_trackloss_rows >= 2)) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  #filter to fixations of at least 12 rows or ~ 200 ms
  filter(n() >= 12) %>%
  filter(target == TRUE) %>%
  group_by(recording_name, trial_number, media_name, looking_stretch_id, initial_look) %>%
  summarise(length_of_looks = n()) %>%
  mutate(duration_of_look = length_of_looks*(1000/60)) %>%
  group_by(recording_name, trial_number, initial_look) %>%
  summarise(duration_of_look = mean(duration_of_look, na.rm = T)) %>%
  ungroup()

mean_fixation_dur_by_subject_split <- mean_fixation_dur_by_trial_split %>% 
  group_by(recording_name, initial_look) %>%
  summarise(duration_of_look = mean(duration_of_look, na.rm = T)) %>%
  ungroup()


#10. Pupil dilation
#Baseline pupil size in the 200ms before noun onset and then subtracted the baseline from the pupil size measurements on each trial.
#In Liz's paper they contrasted time slice by time slice across two conditions, but here we don't have switched and same language conditions. I'll do average size at baseline and avg size after noun onset for now. But then talk with team about it.


pupil_dilation_split <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset>= -200 & noun_onset <= 500)%>%
mutate(pupil_period = case_when(noun_onset >= -200 & noun_onset <= 0 ~ "baseline",
                                TRUE ~ "post_onset"))%>% 
  dplyr::select(recording_timestamp, subject_id, recording_name, trial_number, media_name, pupil_period, pupil_right, pupil_left, initial_look) %>%
  mutate(two_pupil_mean = case_when(is.na(pupil_left) & is.na(pupil_right) ~ NA,
                                         is.na(pupil_left)  ~ pupil_right,
                                         is.na(pupil_right) ~ pupil_left,
                                         TRUE ~ (pupil_left + pupil_right)/2)) %>%
  filter(!is.na(two_pupil_mean))

#The next steps are confusing to me.Should we average baseline pupil? Should we contrast each post onset time slice to a partricular baseline time slice? We could use mean dilation, peak dilation (or peak amplitude), and/or peak latency (i.e., the time between onset and peak pupil dilation). The problem with mean dilation is that the baseline has less sampling than the post-onset. Could we do peak dilation of baseline vs. peak dilation post onset? Or peak dilation but from which baseline point? from peak? We will for sure do GCA's as extra analyses

#Peak dilation
peak_dilation_by_trial_split <- pupil_dilation_split %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period, initial_look) %>%
  summarise(peak_pupil = max(two_pupil_mean)) %>%
  pivot_wider(names_from = pupil_period, values_from ="peak_pupil")%>%
  mutate(peak_pupil_size_difference = post_onset - baseline) %>% #difference in peak pupil points
  filter(!is.na(peak_pupil_size_difference)) %>%
  rename(max_pupil_baseline = baseline,
         max_pupil_post_onset = post_onset) %>%
  ungroup()

peak_dilation_by_subject_split <- peak_dilation_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(peak_pupil_size_difference = mean(peak_pupil_size_difference)) %>%
  ungroup() 
  
#Mean dilation
mean_dilation_by_trial_split <- pupil_dilation_split %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period, initial_look) %>%
  summarise(mean_pupil = mean(two_pupil_mean, na.rm = T)) %>%
  pivot_wider(names_from = pupil_period, values_from ="mean_pupil")%>%
  mutate(mean_pupil_size_difference = post_onset - baseline) %>% #difference in peak pupil points
  filter(!is.na(mean_pupil_size_difference)) %>%
  rename(mean_pupil_baseline = baseline,
         mean_pupil_post_onset = post_onset) %>%
  ungroup() 

mean_dilation_by_subject_split <- mean_dilation_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(mean_pupil_size_difference = mean(mean_pupil_size_difference)) %>%
  ungroup()
  


#peak latency
peak_pupil_latency_by_trial_split <- pupil_dilation_split %>%
  ungroup()%>%
  group_by(trial_number, recording_name, pupil_period) %>%
  slice(which.max(two_pupil_mean)) %>%
  dplyr::select(recording_name, pupil_period, peak_time_stamp = recording_timestamp, initial_look) %>%
  group_by(trial_number, recording_name, initial_look) %>%
  summarise(peak_pupil_latency = diff(peak_time_stamp)) %>%
  ungroup()

peak_pupil_latency_by_subject_split <- peak_pupil_latency_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(peak_pupil_latency = mean(peak_pupil_latency))


#11. Duration of first look
### Duration of the first look recorded toward a particular AOI. - To target specifically, with at least 200 ms fixation length

first_look_duration_by_trial_split <- analysis_dataset %>%
  ungroup() %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  group_by(recording_name, trial_number) %>% 
  mutate(looking_stretch_id = data.table::rleid(target)) %>%
  group_by(recording_name, trial_number, looking_stretch_id) %>%
  mutate(row = row_number()) %>% 
  mutate(where_looking = case_when(target == TRUE ~ "target",
                                   distractor == TRUE ~ "distractor",
                                   TRUE ~ "neither")) %>%
  filter(where_looking == "target") %>%
  mutate(first_look_dur = max(row_number())*(1000/60)) %>% 
  filter(first_look_dur >= 200) %>%
  group_by(trial_number, recording_name) %>%
  filter(looking_stretch_id == min(looking_stretch_id)) %>% 
  ungroup() %>%
  distinct(recording_name, trial_number, media_name, first_look_dur, initial_look) %>%
  ungroup()

first_look_duration_by_subject_split <- first_look_duration_by_trial_split %>%
  group_by(recording_name, initial_look) %>%
  summarise(first_look_dur = mean(first_look_dur, na.rm = T)) %>%
  ungroup()

```

#Add new variables to one dataset
```{r merging newly created DVs to the original dataset}

data_new_dvs_by_trial <- analysis_dataset %>%
  distinct(recording_name, trial_number, yoked_pair, target_word, age_months, exp_to_target_lang) %>%
  left_join(prop_looking_by_trial) %>%
  #double check if kids see the same word more than once... if so, this item will be ducplicated in the dataset
  left_join(prop_looking_diff_by_item) %>%
  # commenting out for now until we verify how to do this one left_join(sampling_fixations_total %>% dplyr::select(-subject_id)) %>%
  left_join(fixations_total_by_trial) %>%
  left_join(prop_shifts_distractor_initial_by_trial) %>%
  left_join(prop_shifts_target_initial_by_subject) %>%
  left_join(RT_by_trial) %>%
  left_join(number_of_switches_by_trial) %>%
  left_join(mean_fixation_dur_by_trial) %>%
  left_join(peak_dilation_by_trial) %>%
  left_join(mean_dilation_by_trial) %>%
  left_join(peak_pupil_latency_by_trial) %>%
  left_join(first_look_duration_by_trial) %>%
  ungroup() %>%
  mutate(exp_to_target_lang_centred = (exp_to_target_lang/100)-.5,
         age_months_centred = age_months - 25,
         correct_shift = case_when(correct_shift == T ~ 1,
                                   correct_shift == F ~ 0))

data_new_dvs_by_subject <- analysis_dataset %>%
  distinct(recording_name, age_months, exp_to_target_lang, fre_exp, eng_exp) %>% #Added french and english exposure to be able to calculate balance for some analyses.
  left_join(prop_looking_by_subject) %>%
  #double check if kids see the same word more than once... if so, this item will be ducplicated in the dataset
  left_join(prop_looking_diff_by_subject) %>%
  # commenting out for now until we verify how to do this one left_join(sampling_fixations_total %>% dplyr::select(-subject_id)) %>%
  left_join(fixations_total_by_subject) %>%
  left_join(prop_shifts_distractor_initial_by_subject) %>%
  left_join(prop_shifts_target_initial_by_subject) %>%
  left_join(RT_by_subject) %>%
  left_join(number_of_switches_by_subject) %>%
  left_join(mean_fixation_dur_by_subject) %>%
  left_join(peak_dilation_by_subject) %>%
  left_join(mean_dilation_by_subject) %>%
  left_join(peak_pupil_latency_by_subject) %>%
  left_join(first_look_duration_by_subject) %>%
  ungroup()%>%
  mutate(exp_to_target_lang_centred = (exp_to_target_lang/100)-.5,
         age_months_centred = age_months - 25)


#How many trials in average when we collapse by subject?

data_new_dvs_by_trial %>%
  group_by(recording_name) %>%
    summarise(num_trials = length(unique(trial_number))) %>%
    summarise(avg_num_trials = mean(num_trials))


```

#Add new split variables to one dataset

```{r}
#this one is for by subject variables only, since by trial would not be different because each trial only has one initial look location value

data_new_dvs_by_subject_split <- analysis_dataset %>%
  distinct(recording_name, age_months, exp_to_target_lang, initial_look) %>%
  left_join(prop_looking_by_subject_split) %>%
  #double check if kids see the same word more than once... if so, this item will be ducplicated in the dataset
  left_join(prop_looking_diff_by_subject_split) %>%
  # commenting out for now until we verify how to do this one left_join(sampling_fixations_total %>% dplyr::select(-subject_id)) %>%
  left_join(fixations_total_by_subject_split) %>%
  left_join(number_of_switches_by_subject_split) %>%
  left_join(mean_fixation_dur_by_subject_split) %>%
  left_join(peak_dilation_by_subject_split) %>%
  left_join(mean_dilation_by_subject_split) %>%
  left_join(peak_pupil_latency_by_subject_split) %>%
  left_join(first_look_duration_by_subject_split) %>%
  ungroup()%>%
  mutate(exp_to_target_lang_centred = (exp_to_target_lang/100)-.5,
         age_months_centred = age_months - 25)

#How many trials in each split of the data?

analysis_dataset_split %>%
  unnest() %>%
  group_by(initial_look, recording_name) %>%
    summarise(num_trials = length(unique(trial_number))) %>%
  group_by(initial_look) %>%
    summarise(avg_num_trials = mean(num_trials))


```


```{r ICC between DVs}


#need to only have the numeric variables for the ICC to be calculated
for_icc <- data_new_dvs_by_subject %>%
  dplyr::select(where(is.numeric)) %>%
   dplyr::select(-c(age_months, exp_to_target_lang, exp_to_target_lang_centred, age_months_centred))

ICC(for_icc, missing = FALSE, lmer = TRUE, alpha=.05)


# ICC for split vriables






```


```{r correlation matrix between DVs}

#Select only numerical variables for correlation

#PEARSON CORRELATION
for_correlation_with_age_lang_centred<- data_new_dvs_by_subject %>%
  dplyr::select(where(is.numeric)) 

for_correlation_no_age_lang_centred<- data_new_dvs_by_subject %>%
  dplyr::select(where(is.numeric)) %>%
  dplyr::select(-contains("centred"))

kbh_correlation <- cor(x=for_correlation_no_age_lang_centred, use="pairwise.complete.obs")

kbh_correlation_2<- rcorr(as.matrix(for_correlation_no_age_lang_centred))

# Extract p-values
p_values <- kbh_correlation_2$P

# Flatten the matrix to adjust p-values
p_values_flat <- as.vector(p_values)

# Adjust p-values using Bonferroni correction
p_values_adj <- p.adjust(p_values_flat, method = "bonferroni")

# Convert the adjusted p-values back to a matrix
p_values_adj_matrix <- matrix(p_values_adj, ncol = ncol(for_correlation_no_age_lang_centred))

test<- as.data.frame(p_values_adj_matrix, options(scipen = 999, digits = 4)) 
  

#plotting the correlation

#Change column and row names to look nicer on plot in real words
colnames(kbh_correlation) <- c("Age in months", "Exposure to target language", "Proportion looking", "Proportion looking difference", "Total number of fixations", "Proportion of trials shifting to target", "Proportion of trials staying on target", "Mean reaction time", "Total number of AOI switches", "Mean duration of looks", "Peak pupil size difference", "Mean pupil size difference", "Time to peak pupil", "Mean duration of first look")
rownames(kbh_correlation) <- c("Age in months", "Exposure to target language", "Proportion looking", "Proportion looking difference", "Total number of fixations", "Proportion of trials shifting to target", "Proportion of trials staying on target", "Mean reaction time", "Total number of AOI switches", "Mean duration of looks", "Peak pupil size difference", "Mean pupil size difference", "Time to peak pupil", "Mean duration of first look")

#Reorder variables so that they apear in my costum order

custom_order<- c("Age in months", "Exposure to target language", "Proportion looking", "Proportion looking difference","Mean reaction time", "Total number of fixations","Peak pupil size difference",  "Mean pupil size difference", "Time to peak pupil", "Proportion of trials shifting to target", "Proportion of trials staying on target","Mean duration of looks", "Mean duration of first look", "Total number of AOI switches")

reordered_kbh_correlation<- kbh_correlation[custom_order, custom_order]

#Create path to save correlation plot as PNG
png(filename= here("archival_KBH_anonimyzed/corrleation.png"),width = 800, height = 800 )

#Plot:
corrplot(reordered_kbh_correlation, type = 'lower', tl.col = 'black',
         cl.ratio = 0.2, tl.srt = 45, col = COL2('PiYG', 10))

#Closing the PNG graphics device.
dev.off()

#Same graph but with pie charts
corrplot(kbh_correlation, method='pie')



#SPEARMAN CORRELATION

kbh_correlation_s <- cor(x=for_correlation, use="pairwise.complete.obs", method = "spearman")



corrplot(kbh_correlation_s)


```


#Factor analysis
```{r}

for_factor_analysis<- for_correlation_with_age_lang_centred %>%
  dplyr::select(-c(age_months, exp_to_target_lang)) %>%
  as.matrix()

for_factor_analysis_noshift <- for_correlation_with_age_lang_centred %>%
  dplyr::select(-c(prop_shift_distractor_initial, prop_shift_target_initial, age_months, exp_to_target_lang)) %>%
  as.matrix()

#We are sticking with ss loads above 1 so that leaves us with 2 factors.
psych::fac(for_factor_analysis, nfactors = 2)

#Mention in a write up that without the only distractor trials the factors are quite similar so we are quite confident it is not an artifact.
psych::fac(for_factor_analysis_noshift, nfactors = 10)


#Proportion looking tends to be good because it considers both distractor initial and target initial trials. But there are other variables like number of fixations that might be good but just for certain types of trials e.g. target initial.

#Pupil is cool as a measure of surprise if they are looking at the wrong thing (distractor initial) but not during target initial trials.

#We want to ultimately give reccomendations. Is there a measure that's more robust, best for manipulations, if it only works for a type of trial, like target initial you are halving your data, so is that best? We might run reliability measures by child by trial.

```







# Models 

Make the following models for each of our variables as the outcome

proportion_looking ~ age + experience + (1|subject) + (1|item)
proportion_looking ~ age + experience + age*experience + (1|subject) + (1|item)

```{r}

#Prop Looking Models
prop_looking_simple <- lm(prop_looking ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(prop_looking_simple)

prop_looking_interaction <- lm (prop_looking ~ age_months_centred*exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(prop_looking_interaction)


#Prop Looking Diff Models
prop_looking_diff_simple <- lm (prop_looking_diff ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(prop_looking_diff_simple)

prop_looking_diff_interaction <- lm (prop_looking_diff ~ age_months_centred*exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(prop_looking_diff_interaction)


#Number fixations Models
number_fixations_simple <- lm (number_fixations ~ age_months_centred + exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(number_fixations_simple)

number_fixations_interaction <- lm (number_fixations ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(number_fixations_interaction)


#Latency to switch Models
latency_to_switch_simple <- lm (mean_RT ~ age_months_centred + exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(latency_to_switch_simple)

latency_to_switch_interaction <- lm (mean_RT ~ age_months_centred*exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(latency_to_switch_interaction)


#Number of AOI switches Models
aoi_switches_simple <- lm (total_aoi_switches ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(aoi_switches_simple)

aoi_switches_interaction <- lm (total_aoi_switches ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(aoi_switches_interaction)

aoi_switches_interaction2 <- lm (total_aoi_switches ~ age_months_centred*exp_to_target_lang, 
                            data = data_new_dvs_by_subject)

interactions::interact_plot(aoi_switches_interaction2, pred= exp_to_target_lang, modx=age_months_centred, plot.points = T)

#Mean fixation duration Models
mean_fixation_dur_simple <- lm (duration_of_look ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(mean_fixation_dur_simple)

mean_fixation_dur_interaction <- lm (duration_of_look ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(mean_fixation_dur_interaction)




#Peak pupil size Models
peak_pupil_simple <- lm (peak_pupil_size_difference ~ age_months_centred + exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(peak_pupil_simple)

peak_pupil_interaction <- lm (peak_pupil_size_difference ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(peak_pupil_interaction)


#Mean pupil size Models
mean_pupil_simple <- lm (mean_pupil_size_difference ~ age_months_centred + exp_to_target_lang_centred,
                            data = data_new_dvs_by_subject)
summary(mean_pupil_simple)

mean_pupil_interaction <- lm (mean_pupil_size_difference ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(mean_pupil_interaction)


#Peak pupil latency Models
peak_pupil_latency_simple <- lm (peak_pupil_latency ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(peak_pupil_latency_simple)

peak_pupil_latency_interaction <- lm (peak_pupil_latency ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(peak_pupil_latency_interaction)


#First look duration Models
first_look_duration_simple <- lm (first_look_dur ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(first_look_duration_simple)

first_look_duration_interaction <- lm (first_look_dur ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(first_look_duration_interaction)


#Correct shift to target models

correct_shift_simple <- lm(prop_shift_distractor_initial ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(correct_shift_simple)

correct_shift_interaction <- lm(prop_shift_distractor_initial ~ age_months_centred*exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)

summary(correct_shift_interaction)


target_stay_simple <-lm(prop_shift_target_initial ~ age_months_centred + exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(target_stay_simple)

target_stay_interaction<- lm(prop_shift_target_initial ~ age_months_centred * exp_to_target_lang_centred, 
                            data = data_new_dvs_by_subject)
summary(target_stay_interaction)


## Contrasting models performance

compare_performance(correct_shift_simple, peak_pupil_latency_simple, mean_pupil_simple, peak_pupil_simple,
                    mean_fixation_dur_simple , aoi_switches_simple, latency_to_switch_simple, prop_looking_diff_simple, number_fixations_simple, prop_looking_simple, target_stay_simple, correct_shift_simple)





```



Models with exposure balance instead of exposure to target language

```{r}
for_balance_models <- data_new_dvs_by_subject %>%
  mutate(balance_score= abs(fre_exp - eng_exp))


#Prop Looking Models
prop_looking_sbalance <- lm(prop_looking ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(prop_looking_sbalance)

prop_looking_ibalance <- lm (prop_looking ~ age_months_centred*balance_score,
                            data = for_balance_models)
summary(prop_looking_ibalance)


#Prop Looking Diff Models
prop_looking_diff_sbalance <- lm (prop_looking_diff ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(prop_looking_diff_sbalance)

prop_looking_diff_ibalance <- lm (prop_looking_diff ~ age_months_centred*balance_score,
                            data = for_balance_models)
summary(prop_looking_diff_ibalance)


#Number fixations Models
number_fixations_sbalance <- lm (number_fixations ~ age_months_centred + balance_score,
                            data = for_balance_models)
summary(number_fixations_sbalance)

number_fixations_ibalance <- lm (number_fixations ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(number_fixations_ibalance)


#Latency to switch Models
latency_to_switch_sbalance <- lm (mean_RT ~ age_months_centred + balance_score,
                            data = for_balance_models)
summary(latency_to_switch_sbalance)

latency_to_switch_ibalance <- lm (mean_RT ~ age_months_centred*balance_score,
                            data = for_balance_models)
summary(latency_to_switch_ibalance)


#Number of AOI switches Models
aoi_switches_sbalance <- lm (total_aoi_switches ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(aoi_switches_sbalance)

aoi_switches_ibalance <- lm (total_aoi_switches ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(aoi_switches_ibalance)


#Mean fixation duration Models
mean_fixation_dur_sbalance <- lm (duration_of_look ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(mean_fixation_dur_sbalance)

mean_fixation_dur_ibalance <- lm (duration_of_look ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(mean_fixation_dur_ibalance)




#Peak pupil size Models
peak_pupil_sbalance <- lm (peak_pupil_size_difference ~ age_months_centred + balance_score,
                            data = for_balance_models)
summary(peak_pupil_sbalance)

peak_pupil_ibalance <- lm (peak_pupil_size_difference ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(peak_pupil_ibalance)


#Mean pupil size Models
mean_pupil_sbalance <- lm (mean_pupil_size_difference ~ age_months_centred + balance_score,
                            data = for_balance_models)
summary(mean_pupil_sbalance)

mean_pupil_ibalance <- lm (mean_pupil_size_difference ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(mean_pupil_ibalance)


#Peak pupil latency Models
peak_pupil_latency_sbalance <- lm (peak_pupil_latency ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(peak_pupil_latency_sbalance)

peak_pupil_latency_ibalance <- lm (peak_pupil_latency ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(peak_pupil_latency_ibalance)


#First look duration Models
first_look_duration_sbalance <- lm (first_look_dur ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(first_look_duration_sbalance)

first_look_duration_ibalance <- lm (first_look_dur ~ age_months_centred*balance_score, 
                            data = for_balance_models)
summary(first_look_duration_sbalance)


#Correct shift to target models

correct_shift_sbalance <- lm(prop_shift_distractor_initial ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(correct_shift_sbalance)

correct_shift_ibalance <- lm(prop_shift_distractor_initial ~ age_months_centred*balance_score, 
                            data = for_balance_models)

summary(correct_shift_ibalance)


target_stay_sbalance <-lm(prop_shift_target_initial ~ age_months_centred + balance_score, 
                            data = for_balance_models)
summary(target_stay_sbalance)

target_stay_ibalance<- lm(prop_shift_target_initial ~ age_months_centred * balance_score, 
                            data = for_balance_models)
summary(target_stay_ibalance)


## Contrasting models performance

compare_performance(correct_shift_sbalance, peak_pupil_latency_sbalance, mean_pupil_sbalance, peak_pupil_sbalance,
                    mean_fixation_dur_sbalance , aoi_switches_sbalance, latency_to_switch_sbalance, prop_looking_diff_sbalance, number_fixations_sbalance, prop_looking_sbalance, target_stay_sbalance, correct_shift_sbalance)










```


## Models with split data

```{r}

#Models in nested dataframe

model_data_nested <- data_new_dvs_by_subject_split %>%
  group_by(initial_look) %>%
  nest() 

models_nested <- model_data_nested %>%
  mutate(
    #Prop looking
    prop_looking_simple_split = map(data, ~lm(prop_looking ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #Prop looking diff
         prop_looking_diff_simple_split = map(data, ~lm (prop_looking_diff ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #Number fixations
    number_fixations_simple_split = map(data, ~lm (number_fixations ~ age_months_centred + exp_to_target_lang_centred,
                            data = .x)),
    #Latency to switch
    # latency_to_switch_simple_split = map(data, ~ lm(mean_RT ~ age_months_centred + exp_to_target_lang_centred,
    #                         data = .x)),
    #Number AOI switches
    aoi_switches_simple_split = map(data, ~ lm(total_aoi_switches ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #Mean fixation duration
    mean_fixation_dur_simple_split = map(data, ~lm(duration_of_look ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #Peak pupil size
    peak_pupil_simple_split = map(data, ~lm(peak_pupil_size_difference ~ age_months_centred + exp_to_target_lang_centred,
                            data = .x)),
    #Mean pupil size
    mean_pupil_simple_split = map(data, ~lm(mean_pupil_size_difference ~ age_months_centred + exp_to_target_lang_centred,
                            data = .x)),
    #Peak pupil latency
    peak_pupil_latency_simple_split = map(data, ~lm(peak_pupil_latency ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #First look duration
    first_look_duration_simple_split = map(data, ~lm(first_look_dur ~ age_months_centred + exp_to_target_lang_centred, 
                            data = .x)),
    #Correct shift for distractor initial 
    # correct_shift_simple_split = map(data, ~lm(prop_shift_distractor_initial ~ age_months_centred + exp_to_target_lang_centred, 
    #                         data = .x)),
    # #Staying on target for target initial
    # target_stay_simple_split = map(data, ~lm(prop_shift_target_initial ~ age_months_centred + exp_to_target_lang_centred, 
    #                         data = .x))
         )


## Contrasting models performance

compare_performance(correct_shift_simple , peak_pupil_latency_simple, mean_pupil_simple, peak_pupil_simple,
                    mean_fixation_dur_simple , aoi_switches_simple, latency_to_switch_simple, prop_looking_diff_simple, number_fixations_simple, prop_looking_simple, target_stay_simple, correct_shift_simple)


models_nested_long <- models_nested %>%
  pivot_longer(contains("split"), names_to = "model_name", values_to = "model_object") %>%
  group_by(initial_look) %>%
  nest() 

#Target initial
compare_performance(models_nested_long$data[[1]]$model_object)
#Distractor initial
compare_performance(models_nested_long$data[[2]]$model_object)
#Neither initial
compare_performance(models_nested_long$data[[3]]$model_object)


#Model summaries

models_nested_long %>%
  unnest() %>%
  mutate(model_summary = map(model_object, ~summary(.x))) %>%
  pull(model_summary)

```
#Check plot
```{r}

#Let's plot raw data split by initial look to make sure models make sense

data_for_check_plot <- analysis_dataset %>%
  filter(noun_onset >= 360 & noun_onset <= 3000) %>%
  make_eyetrackingr_data(., 
                               participant_column = "recording_name",
                               trial_column = "trial_number",
                               time_column = "noun_onset",
                               trackloss_column = "trackloss",
                               aoi_columns = c('target','distractor'),
                               treat_non_aoi_looks_as_missing = TRUE)
  
  
data_for_check_plot %>%
  make_time_sequence_data(., time_bin_size = 100, aois = NULL,
  predictor_columns = c("initial_look"), other_dv_columns = NULL, summarize_by = c("recording_name", "trial_number")) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = AOI)) +
  geom_jitter(alpha = .1, height = .025) +
  geom_smooth() +
  facet_wrap(~initial_look)

#The looking time sequence for target-initial trials seems to have a shallow drop in looking to target over the course of the interest period, as opposed to a sharp rise for distractor-initial trials. This might help explain some of the model differences in significance after splitting by initial look location.


```

